### 2024-07-16 doc/src/vtr/vtr_flow_fig.tex

    \matrix [row sep=0.6cm, column sep=0.9cm] {
        \node (arch) [device] {FPGA \\ Architecture}; & & \node (hdl) [design] {HDL}; & \\
        & \node (odin_synth) [process] {Odin II}; & \node (quartus_map) [process] {Quartus \\ Map}; & \node (yosys_frontend) [] {Yosys}; \\
        & & \node (vqm2blif) [process] {VQM to BLIF}; & \node (abc_yosys) [process_no_shadow] {ABC}; \\
        & \node (abc_synth) [process] {ABC}; & & \\
        & & \node (techmapped_netlist) [design] {Tech. Mapped \\ Netlist}; & & \\
        & \node (vpr_pack) [process] {VPR \\ Pack}; & \node (packing) [design] {Packing}; & \node (other_pack) [process, dashed] {Other \\ Pack}; & \\
        & \node (vpr_place) [process] {VPR \\ Place}; & \node (placement) [design] {Placement}; & \node (other_place) [process, dashed] {Other \\ Place}; & \\
        & \node (vpr_route) [process] {VPR \\ Route}; & \node (routing) [design] {Routing}; & \node (other_route) [process, dashed] {Other \\ Route}; & \\
        & & & & \\
        & \node (vpr_analysis) [process] {VPR \\ Analysis}; & & \node (assembler) [process, dashed] {Bitstream Gen.}; & \\
    };
    \node(rr_graph) [device,left=0.25cm of arch] {RR-Graph};

@@

    \draw [arrow] (arch) |- (odin_synth);
    \draw [arrow] (arch) |- (vpr_pack.west);
    \draw [arrow] (arch) |- ([yshift=\arrowshift]vpr_place.west);
    \draw [arrow] (arch) |- ([yshift=\arrowshift]vpr_route.west);
    \draw [arrow] (arch) |- ([yshift=\arrowshift]vpr_analysis.west);
    \draw [arrow] (arch) |- ([yshift=\arrowshift]vpr_analysis.west);

    \draw [arrow] (hdl) -- (odin_synth.north);
    \draw [arrow] (hdl) -- (quartus_map);
    \draw [arrow] (hdl) -- (yosys.north);
    \draw[arrow] (odin_synth) -- (abc_synth);
    \draw[arrow] (quartus_map) -- (vqm2blif);
    \draw[arrow] (yosys) |- ([yshift=\arrowshift,xshift=\arrowxshift]techmapped_netlist.east);
    \draw[arrow] (vqm2blif) -- (abc_synth);
    \draw[arrow] (vqm2blif) -- (techmapped_netlist);
    \draw[arrow] (abc_synth) |- ([yshift=\arrowshift,xshift=\arrowxshift]techmapped_netlist.west);

@@

    \begin{scope}[on background layer]
        %VTR Callout
        \draw[vtr_callout]
            ([xshift=-\vtroffset,yshift=\vtroffset]odin_synth.north west)
         -- ([xshift=-\vtroffset,yshift=-\vtroffset]vpr_analysis.south west)
         -- ([xshift=\vtroffset,yshift=-\vtroffset]vpr_analysis.south east)
         -- ([xshift=\vtroffset,yshift=-\vtroffset]vpr_pack.north east)
         -- ([xshift=-\vtroffset,yshift=-\vtroffset]techmapped_netlist.bottom left corner-|techmapped_netlist.bottom left corner)
         -- ([xshift=\vtroffset,yshift=-\vtroffset]techmapped_netlist.bottom right corner-|techmapped_netlist.top right corner)
         -- ([xshift=\vtroffset,yshift=\vtroffset]techmapped_netlist.top right corner)
         -- ([xshift=\vtroffset,yshift=\vtroffset]techmapped_netlist.top left corner-|abc_synth.south east)
         -- ([xshift=\vtroffset,yshift=\vtroffset]abc_synth.south east)
         -- ([xshift=\vtroffset,yshift=\vtroffset]odin_synth.north east)
         -- cycle;

>>>>

    \matrix [row sep=0.6cm, column sep=0.9cm] {
        \node (arch) [device] {FPGA \\ Architecture}; & & \node (hdl) [design] {HDL}; & \\
        & \node (parmys_synth) [process] {Parmys}; & \node (quartus_map) [process] {Quartus \\ Map}; & \node (yosys_frontend) [] {Yosys}; \\
        & & \node (vqm2blif) [process] {VQM to BLIF}; & \node (abc_yosys) [process_no_shadow] {ABC}; \\
        & \node (abc_synth) [process] {ABC}; & & \\
        & & \node (techmapped_netlist) [design] {Tech. Mapped \\ Netlist}; & & \\
        & \node (vpr_pack) [process] {VPR \\ Pack}; & \node (packing) [design] {Packing}; & \node (other_pack) [process, dashed] {Other \\ Pack}; & \\
        & \node (vpr_place) [process] {VPR \\ Place}; & \node (placement) [design] {Placement}; & \node (other_place) [process, dashed] {Other \\ Place}; & \\
        & \node (vpr_route) [process] {VPR \\ Route}; & \node (routing) [design] {Routing}; & \node (other_route) [process, dashed] {Other \\ Route}; & \\
        & & & & \\
        & \node (vpr_analysis) [process] {VPR \\ Analysis}; & & \node (assembler) [process, dashed] {Bitstream Gen.}; & \\
    };
    \node(rr_graph) [device,left=0.25cm of arch] {RR-Graph};

@@

    \draw [arrow] (arch) |- (parmys_synth);
    \draw [arrow] (arch) |- (vpr_pack.west);
    \draw [arrow] (arch) |- ([yshift=\arrowshift]vpr_place.west);
    \draw [arrow] (arch) |- ([yshift=\arrowshift]vpr_route.west);
    \draw [arrow] (arch) |- ([yshift=\arrowshift]vpr_analysis.west);
    \draw [arrow] (arch) |- ([yshift=\arrowshift]vpr_analysis.west);

    \draw [arrow] (hdl) -- (parmys_synth.north);
    \draw [arrow] (hdl) -- (quartus_map);
    \draw [arrow] (hdl) -- (yosys.north);
    \draw[arrow] (parmys_synth) -- (abc_synth);
    \draw[arrow] (quartus_map) -- (vqm2blif);
    \draw[arrow] (yosys) |- ([yshift=\arrowshift,xshift=\arrowxshift]techmapped_netlist.east);
    \draw[arrow] (vqm2blif) -- (abc_synth);
    \draw[arrow] (vqm2blif) -- (techmapped_netlist);
    \draw[arrow] (abc_synth) |- ([yshift=\arrowshift,xshift=\arrowxshift]techmapped_netlist.west);

@@

    \begin{scope}[on background layer]
        %VTR Callout
        \draw[vtr_callout]
            ([xshift=-\vtroffset,yshift=\vtroffset]parmys_synth.north west)
         -- ([xshift=-\vtroffset,yshift=-\vtroffset]vpr_analysis.south west)
         -- ([xshift=\vtroffset,yshift=-\vtroffset]vpr_analysis.south east)
         -- ([xshift=\vtroffset,yshift=-\vtroffset]vpr_pack.north east)
         -- ([xshift=-\vtroffset,yshift=-\vtroffset]techmapped_netlist.bottom left corner-|techmapped_netlist.bottom left corner)
         -- ([xshift=\vtroffset,yshift=-\vtroffset]techmapped_netlist.bottom right corner-|techmapped_netlist.top right corner)
         -- ([xshift=\vtroffset,yshift=\vtroffset]techmapped_netlist.top right corner)
         -- ([xshift=\vtroffset,yshift=\vtroffset]techmapped_netlist.top left corner-|abc_synth.south east)
         -- ([xshift=\vtroffset,yshift=\vtroffset]abc_synth.south east)
         -- ([xshift=\vtroffset,yshift=\vtroffset]parmys_synth.north east)
         -- cycle;

### 2024-07-16 doc/src/vtr/vtr_task_fig.tex

    \node[run_result, below=\levelspace of params1] (result1) {\makecell{odin.out \\ abc.out \\ vpr.out}};
    \node[run_result, below=\levelspace of params2] (result2) {\makecell{odin.out \\ abc.out \\ vpr.out}};

>>>>

    \node[run_result, below=\levelspace of params1] (result1) {\makecell{parmys.out \\ abc.out \\ vpr.out}};
    \node[run_result, below=\levelspace of params2] (result2) {\makecell{parmys.out \\ abc.out \\ vpr.out}};
